Supplementary Figure 1f

### 2017-11-20 inst/cellular_localization/cellular_localization.Rmd
commenting ggsave in Rmds

figure <- plotPDF(p)
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1e"][[1]])

ggsave(
 plot = figure,
 filename = path,
 device = cairo_pdf,
 height = 60,
 width = 83,
 units = "mm"
)
```

>>>>

figure <- plotPDF(p)

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1e"][[1]])
# ggsave(
#  plot = figure,
#  filename = path,
#  device = cairo_pdf,
#  height = 60,
#  width = 83,
#  units = "mm"
# )
```

### 2017-11-20 inst/hct116_hek293t_dox/hct116_hek293t_dox.Rmd
commenting ggsave in Rmds

figure <- plotPDF(pdf)
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2b"][[1]])

ggsave(
   plot = figure,
   filename = path,
   device = cairo_pdf,
   height = 60,
   width = 83,
   units = "mm"
)
```

>>>>

figure <- plotPDF(pdf)

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2b"][[1]])
# ggsave(
#    plot = figure,
#    filename = path,
#    device = cairo_pdf,
#    height = 60,
#    width = 83,
#    units = "mm"
# )
```

### 2017-11-20 inst/hct116_p53_null/hct116_p53_null.Rmd
commenting ggsave in Rmds

figure <- plotPDF(pdf)
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2a"][[1]])

ggsave(
 plot = figure,
 filename = path,
 device = cairo_pdf,
 height = 60,
 width = 83,
 units = "mm"
)
```

>>>>

figure <- plotPDF(pdf)

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2a"][[1]])
# ggsave(
#  plot = figure,
#  filename = path,
#  device = cairo_pdf,
#  height = 60,
#  width = 83,
#  units = "mm"
# )
```

### 2017-11-20 inst/lnc34a_cage/lnc34a_cage.Rmd
commenting ggsave in Rmds

path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2d"][[1]])

ggsave(
  plot = g, 
  filename = path, 
  device = cairo_pdf, 
  height = 60,
  width = 83,
  units = "mm"
)
```

>>>>

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2d"][[1]])
# ggsave(
#   plot = g, 
#   filename = path, 
#   device = cairo_pdf, 
#   height = 60,
#   width = 83,
#   units = "mm"
# )
```

### 2017-11-20 inst/lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd
commenting ggsave in Rmds

path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2e"][[1]])

ggsave(
  plot = g, 
  filename = path, 
  device = cairo_pdf, 
  height = 60,
  width = 83,
  units = "mm"
)

>>>>

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2e"][[1]])
# ggsave(
#   plot = g, 
#   filename = path, 
#   device = cairo_pdf, 
#   height = 60,
#   width = 83,
#   units = "mm"
# )
```

### 2017-11-20 inst/p1_hct116_hek293t/p1_hct116_hek293t.Rmd
commenting ggsave in Rmds

figure <- plotPDF(pdf)
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2d"][[1]])

ggsave(
   plot = figure,
   filename = path,
   device = cairo_pdf,
   height = 60,
   width = 83,
   units = "mm"
)
```

>>>>

figure <- plotPDF(pdf)

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2d"][[1]])
# ggsave(
#    plot = figure,
#    filename = path,
#    device = cairo_pdf,
#    height = 60,
#    width = 83,
#    units = "mm"
# )
```

### 2017-11-20 inst/p1_shrna_renilla_dox/p1_shrna_renilla_dox.Rmd
commenting ggsave in Rmds

figure <- plotPDF(pdf)
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2e"][[1]])

ggsave(
   plot = figure,
   filename = path,
   device = cairo_pdf,
   height = 60,
   width = 83,
   units = "mm"
)
```

>>>>

figure <- plotPDF(pdf)

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2e"][[1]])
# ggsave(
#    plot = figure,
#    filename = path,
#    device = cairo_pdf,
#    height = 60,
#    width = 83,
#    units = "mm"
# )
```

### 2017-11-20 inst/stable_line_ccnd1_exp/stable_line_ccnd1_exp.Rmd
commenting ggsave in Rmds

figure <- plotPDF(pdf)
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2b"][[1]])

ggsave(
 plot = figure,
 filename = path,
 device = cairo_pdf,
 height = 60,
 width = 43,
 units = "mm"
)
```

>>>>

figure <- plotPDF(pdf)

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2b"][[1]])
# ggsave(
#  plot = figure,
#  filename = path,
#  device = cairo_pdf,
#  height = 60,
#  width = 43,
#  units = "mm"
# )
```

### 2017-11-20 inst/stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd
commenting ggsave in Rmds

path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2c"][[1]])
ggsave(
  plot = figure, 
  filename = path, 
  device = cairo_pdf, 
  height = 60,
  width = 43,
  units = "mm"
)
```

>>>>

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2c"][[1]])
# ggsave(
#   plot = figure, 
#   filename = path, 
#   device = cairo_pdf, 
#   height = 60,
#   width = 43,
#   units = "mm"
# )
```

### 2017-11-20 inst/stable_line_cell_cycle/stable_line_cell_cycle.Rmd
commenting ggsave in Rmds

#url <- "figure3b_stableLineCellCycle.rds"
#data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

figure <- plotPDF(pdf)
#path <- "~/GitHub/miR34a_asRNA_project/inst/figure3b_stableLineCellCycle/figure3b_stableLineCellCycle.pdf"
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3b"][[1]])

ggsave(
   plot = figure,
   filename = path,
   device = cairo_pdf,
   height = 60,
   width = 83,
   units = "mm"
)
```

>>>>

@@

figure <- plotPDF(pdf)

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3b"][[1]])
# ggsave(
#    plot = figure,
#    filename = path,
#    device = cairo_pdf,
#    height = 60,
#    width = 83,
#    units = "mm"
# )
```

### 2017-11-20 inst/stable_line_expression/stable_line_expression.Rmd
commenting ggsave in Rmds

figure <- plotPDF(pdf)
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3a"][[1]])

ggsave(
   plot = figure,
   filename = path,
   device = cairo_pdf,
   height = 60,
   width = 83,
   units = "mm"
)
```

>>>>

figure <- plotPDF(pdf)

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3a"][[1]])
# ggsave(
#    plot = figure,
#    filename = path,
#    device = cairo_pdf,
#    height = 60,
#    width = 83,
#    units = "mm"
# )
```

### 2017-11-20 inst/stable_line_expression_hek293t/stable_line_expression_hek293t.Rmd
commenting ggsave in Rmds

figure <- plotPDF(pdf)
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2a"][[1]])

ggsave(
 plot = figure,
 filename = path,
 device = cairo_pdf,
 height = 60,
 width = 130,
 units = "mm"
)
```

>>>>

figure <- plotPDF(pdf)

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2a"][[1]])
# ggsave(
#  plot = figure,
#  filename = path,
#  device = cairo_pdf,
#  height = 60,
#  width = 130,
#  units = "mm"
# )
```

### 2017-11-20 inst/stable_line_growth_starvation/stable_line_growth_starvation.Rmd
commenting ggsave in Rmds

figure <- plotPDF(pdf)
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3c"][[1]])

ggsave(
  plot = figure,
  filename = path,
  device = cairo_pdf,
  height = 60,
  width = 83,
  units = "mm"
)
```

>>>>

figure <- plotPDF(pdf)

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3c"][[1]])
# ggsave(
#   plot = figure,
#   filename = path,
#   device = cairo_pdf,
#   height = 60,
#   width = 83,
#   units = "mm"
# )
```

### 2017-11-20 inst/stable_line_pol2_chip/stable_line_pol2_chip.Rmd
commenting ggsave in Rmds

figure <- plotPDF(pdf)
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3d"][[1]])

ggsave(
  plot = figure,
  filename = path,
  device = cairo_pdf,
  height = 60,
  width = 43,
  units = "mm",
  dpi = 10000000
)
```

>>>>

figure <- plotPDF(pdf)

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3d"][[1]])
# ggsave(
#   plot = figure,
#   filename = path,
#   device = cairo_pdf,
#   height = 60,
#   width = 43,
#   units = "mm",
#   dpi = 10000000
# )
```

### 2017-11-20 inst/transcript_stability/transcript_stability.Rmd
commenting ggsave in Rmds

figure <- plotPDF(pdf)
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1f"][[1]])

ggsave(
 plot = figure,
 filename = path,
 device = cairo_pdf,
 height = 60,
 width = 83,
 units = "mm"
)
```

>>>>

figure <- plotPDF(pdf)

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1f"][[1]])
# ggsave(
#  plot = figure,
#  filename = path,
#  device = cairo_pdf,
#  height = 60,
#  width = 83,
#  units = "mm"
# )
```
